Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-11-13 paper/tex/introduction.tex

As an example, in order for \pz\ systematics to not dominate the statistical noise floor of \lsst's main cosmological sample of several $10^{9}$ galaxies, the \lsst\ Science Requirements Document (SRD)\footnote{available at \url{https://docushare.lsstcorp.org/docushare/dsweb/Get/LPM-17}} specifies that individual galaxy \pz s must have root-mean-square error $\sigma_z < 0.02 (1+z)$, $3 \sigma$ catastrophic outlier rate below $10\%$, and bias below $0.003$.
Specific science cases may have their own requirements on \pz\ performance that exceed those of the survey as a whole.
In that vein, the \lsst\ Dark Energy Science Collaboration (\lsstdesc) developed a separate SRD \citep{Mandelbaum:2018} that conservatively forecasts the constraining power of five cosmological probes, leading to even more stringent requirements on \pz\ performance, including those defined in terms of tomographically binned subsample populations rather than individual galaxies.

>>>>

As an example, in order for \pz\ systematics to not dominate the statistical noise floor of \lsst's main cosmological sample of several $10^{9}$ galaxies, the \lsst\ Science Requirements Document (SRD)\footnote{available at \url{https://docushare.lsstcorp.org/docushare/dsweb/Get/LPM-17}} specifies that individual galaxy \pz s must have root-mean-square error $\sigma_z < 0.02 (1+z)$, $3 \sigma$ catastrophic outlier rate below $10\%$, and bias below $0.003$.
Specific science cases may have their own requirements on \pz\ performance that exceed those of the survey as a whole.
In that vein, the \lsst\ Dark Energy Science Collaboration (\lsstdesc) developed a separate SRD \citep{Mandelbaum:2018} that conservatively forecasts the constraining power of five cosmological probes, leading to even more stringent requirements on \pz\ performance, including those defined in terms of tomographically binned subsamples populations rather than individual galaxies.
